\documentclass[11pt,english]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{titling}
\usepackage[a4paper,top=2cm,bottom=2cm,left=2.5cm,right=2.5cm]{geometry}
\usepackage{enumitem}

% Page style
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\headheight}{20pt}

\begin{document}

%-------------------------------------------------------%
\title{\textbf{Survey - Student Use of Investment Platforms}}
\date{}
\maketitle
\vspace{-7em}
\thispagestyle{fancy}

\noindent
\textbf{Purpose:} \\
This study will explore how University of Exeter students use investment platforms and how
their financial and digital literacy affect their investment behaviour. It is anonymous and will
take no longer than 5 minutes to complete.

\vspace{-1em}

%-------------------------------------------------------%
\section*{Section 1 – Background}

\begin{enumerate}[leftmargin=1.5em,label=\textbf{\arabic*.}]
\item \textbf{Year of study:} \\
$\square$ 1st year \quad $\square$ 2nd year \quad $\square$ 3rd year \quad $\square$ Postgraduate

\item \textbf{Field of study:} \\
$\square$ Business / Economics \quad $\square$ Engineering / Science \quad $\square$ Humanities / Arts \quad $\square$ Other

\item \textbf{Have you ever used an investment platform (e.g. Vanguard, eToro, Trading212)?} \\
$\square$ Yes \quad $\square$ No

\item \textbf{How long have you been investing?} \\
$\square$ Less than 6 months \quad $\square$ 6–12 months \quad $\square$ 1–2 years \quad $\square$ Over 2 years

\item \textbf{Which type of platform have you mainly used?} \\
$\square$ Trading app (e.g. Trading212, Vanguard) \quad $\square$ Robo-advisor (e.g. Moneybox, Nutmeg) \quad $\square$ Other
\end{enumerate}

\vspace{0.5em}
\hrule
\vspace{0.8em}

%-------------------------------------------------------%
\section*{Section 2 – Financial Literacy}

\begin{enumerate}[resume,leftmargin=1.5em,label=\textbf{\arabic*.}]
\item \textbf{How confident are you in understanding key financial terms such as ``risk'' and ``diversification''?} \\
$\square$ Not confident \quad $\square$ Somewhat confident \quad $\square$ Confident \quad $\square$ Very confident

\item \textbf{If you invest £100 per month into a fund that returns 10\% annually, after 30 years, the majority of your total balance will come from:} \\
$\square$ Capital (Your Investment) \quad $\square$ Compound interest/growth \quad $\square$ Will be equal \quad $\square$ Not Sure

\item \textbf{If prices increase by 3\% but your savings earn 1\% interest, what happens to your purchasing power?} \\
$\square$ It increases \quad $\square$ It stays the same \quad $\square$ It decreases \quad $\square$ Not sure

\item \textbf{Investing in a single company's stock is generally:} \\
$\square$ Less risky \quad $\square$ As risky \quad $\square$ More risky than investing in a diversified fund \quad $\square$ Not sure

\item \textbf{Which statement best describes the relationship between risk and reward in investing?} \\
$\square$ Higher risk generally leads to lower potential reward \quad $\square$ Higher risk generally leads to higher potential reward \quad $\square$ Risk and reward are not related \quad $\square$ Not sure

\item \textbf{If you were offered £100 today or £110 in one year, which is generally better if inflation is 5\%?} \\
$\square$ £100 today \quad $\square$ £110 in one year \quad $\square$ No difference \quad $\square$ Not sure

\item \textbf{What is the primary purpose of diversification in a stock portfolio?} \\
$\square$ To guarantee higher overall returns \quad $\square$ To minimize fees and expenses \quad $\square$ To reduce the overall risk of the portfolio \quad $\square$ Not sure

\item \textbf{If the current UK inflation rate is 10\%, how much interest would a savings account need to pay to preserve your purchasing power?} \\
$\square$ Exactly 0\% interest \quad $\square$ Less than 10\% interest \quad $\square$ Exactly $10\%$ interest \quad $\square$ Not sure

\item \textbf{Do you think your financial knowledge has improved since using an investment platform?} \\
$\square$ No \quad $\square$ Slightly \quad $\square$ Moderately \quad $\square$ Significantly

\end{enumerate}

\vspace{0.5em}
\hrule
\vspace{0.8em}

%-------------------------------------------------------%
\section*{Section 3 – Digital Literacy}

\begin{enumerate}[resume,leftmargin=1.5em,label=\textbf{\arabic*.}]
\item \textbf{How confident are you in accurately interpreting graphs and data visualisations on investment platforms?} \\
$\square$ Not confident \quad $\square$ Somewhat confident \quad $\square$ Confident \quad $\square$ Very confident

\item \textbf{Which platform features do you use most often?} \\
$\square$ Portfolio analytics \quad $\square$ Stock performance charts \quad $\square$ Market news \quad $\square$ AI or data insights \quad $\square$ Other

\item \textbf{Have you ever made a financial decision you later regretted because you misinterpreted data on an app?} \\
$\square$ Yes \quad $\square$ No \quad $\square$ Not sure
\end{enumerate}

\vspace{0.5em}
\hrule
\vspace{0.8em}

%-------------------------------------------------------%
\section*{Section 4 – Investment Behaviour \& Attitudes}

\begin{enumerate}[resume,leftmargin=1.5em,label=\textbf{\arabic*.}]
\item \textbf{How often do you make investment decisions mainly based on app data (e.g. charts, performance metrics)?} \\
$\square$ Never \quad $\square$ Rarely \quad $\square$ Sometimes \quad $\square$ Often \quad $\square$ Always

\item \textbf{When making investment decisions, which influences you more?} \\
$\square$ Data and analytics \quad $\square$ Social media trends \quad $\square$ Advice from others \quad $\square$ Personal decisions

\item \textbf{Do you think investment apps oversimplify complex financial data?} \\
$\square$ Strongly disagree \quad $\square$ Disagree \quad $\square$ Neutral \quad $\square$ Agree \quad $\square$ Strongly agree

\item \textbf{How likely are you to use new features (AI insights or auto-suggested portfolios)?} \\
$\square$ Very unlikely \quad $\square$ Unlikely \quad $\square$ Neutral \quad $\square$ Likely \quad $\square$ Very likely

\item \textbf{To what extent do you believe that access to data visualisations helps you make better investment decisions?} \\
$\square$ Strongly disagree \quad $\square$ Disagree \quad $\square$ Neutral \quad $\square$ Agree \quad $\square$ Strongly agree
\end{enumerate}

\vspace{1.5em}
\noindent\textit{Thank you for taking the time to complete this survey. Your responses will help inform research on how students engage with investment data and analytics.
. If you have found any of these questions distressing, reach out to the University Support Services for assistance.}

\end{document}
